\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-26 paper.tex
Update on Overleaf.

\subsubsection{Physics simulation}

@@

\uwds has been used within the European MuMMER project
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{laasudws}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}
The interaction scenario requires a number of \uwds clients. The clients are
distributed across...

Figure~\ref{fig|mummerarchitecture} illustrates the topology of
the \uwds network...

>>>>

\subsubsection{Physics simulation}\label{physics}

@@

%\uwds has been used within the European MuMMER project
%in order to conceptualise and visualise the spatial relations and visibility of
%the physical objects that participants interact with.

%TODO LAAS

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{laasudws}
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in
    the MuMMER project. }
    \label{fig|mummerarchitecture}
\end{figure}
%The interaction scenario requires a number of \uwds clients. The clients are
%distributed across...

Figure~\ref{fig|mummerarchitecture} illustrates the topology of
the \uwds network. A first client \textit{env\_provider} provides the environment set-up and allows to build a first \texttt{ENV} world where static objects/furnitures and walls are present. 
Then, the system cascades three worlds successively by the help of three clients. \textit{robot\_monitor} provides a first world where the robot is present. \textit{humans\_monitor} provides a new world where the humans are present. \textit{object\_monitor} provides a new world where the objects are present. At this end we obtain a world \texttt{BASE}.

This world \texttt{BASE} is then passed through a \textit{physics filter} client as explained in section \ref{physics} to obtain a \texttt{STABLE} world where all elements are present and consistent: robot, humans, objects and static environment. On this world, we use \textit{Computation of spatial relations} client to get information such as onTop, isIn or isAbove.

This world \texttt{STABLE} is then used by a \textit{perspective filter} client to provide different perspectives given the monitored agent (in our case: human 1, human 2 or the robot itself). Besides giving a view of the input world in the perspective of the monitored agent, it aggregates all the information gathered by this agent. Consequently, it does not offer a snapshot of the agent belief at a particular time but an aggregated version along the time.
